The relative roles of genetic, ecological and environmental factors in insular species radiations

### 2018-07-03 paper/draft.tex
add remark to species concepts in disc

\printbibliography

>>>>

It should be noted that observed speciation and radiation events hinge upon arbitrary species concepts.
Increasingly more available population genome data make apparent that population genetic structure does not
always mirror classic systematics.
Therefore, we expect future studies to continue focussing on population level variablity when conducting genetic analyses.
\printbibliography
